Noncoherent least squares estimators of carrier phase and amplitude

### 2012-10-25 other/confnoncoherent/paper.tex
minor

We will have particular use of complex random variables of the form $1 + X$ where $X$ is circularly symmetric.  Let $R \geq 0$ and $\Phi \in [0,2\pi)$ be real random variables satisfying 
\[
R e^{j\Phi} = 1 + X.
\]
The joint distribution of $R$ and $\Phi$ can be shown to be
\[
f(r,\phi) = \frac{r f_Z(\sqrt{r^2 - 2r\cos\phi + 1})}{2\pi\sqrt{r^2 - 2r\cos\phi + 1}}.
\]

@@

A key assumption in Theorem~\ref{thm:consistency} is that $G(x)$ is uniquely maximised at $x = 0$ for $x \in [-\pi, \pi)$.  %This assumption asserts that $G(x) \leq G(0)$ for all $x \in [-\pi, \pi)$ and that if $\{x_i\}$ is a sequence of numbers from $[-\pi,\pi)$ such that $G(x_i) \rightarrow G(0)$ as $i \rightarrow \infty$ then $x_i \rightarrow 0$ as $i \rightarrow \infty$.  
Although we will not prove it here, this assumption is not only sufficient, but also necessary, for if $G(x)$ is uniquely maximised at some $x \neq 0$ then $\sfracpart{\theta_0 - \hat{\theta}}_\pi \rightarrow x$ almost surely as $L\rightarrow\infty$, while if $G(x)$ is not uniquely maximised then $\sfracpart{\theta_0 - \hat{\theta}}_\pi$ will not converge.  
%The next proposition describes a class of circularly symmetric distributions for which $G(x)$ is uniquely maximised at $x = 0$.  The zero mean complex Gaussian distribution with independent real and imaginary parts is in this class.  We omit the proof due to space constraints.

@@

Let the noise sequence $\{w_i\}$ be complex Gaussian with independent real and imaginary parts having zero mean and variance $\sigma^2$.  The joint pdf of the real and imaginary parts is
\[
p(x,y) = \frac{1}{2\pi\sigma^2}e^{-(x^2 + y^2)/\sigma^2}.
\]
Theorem~\ref{thm:consistency}~and~\ref{thm:normality} hold and, since the distribution of $w_1$ is circularly symmetric, the distribution of $R_1e^{j\Phi_1}$ is identical to the distribution of $1 + \frac{1}{\rho_0} w_1$.
%and the joint density function of the real and imaginary parts of $Z$ is
%\[
%p_Z(x,y) = \rho_0^2 p( \rho_0 (x - 1), \rho_0 y ) = \frac{\kappa^2}{2\pi}e^{-\kappa^2(x ^2 - 2x + 1 + y^2) }
%\] 
%where $\kappa = \tfrac{\rho_0}{\sigma}$.  
It can be shown that
\[
g(\phi) = \frac{\cos^2(\phi)}{4\sqrt{\pi}}\left( \frac{e^{-\kappa^2} }{\sqrt{\pi}} + \kappa \Psi(\phi)  e^{-\kappa^2\sin^2(\phi)}\cos(\phi) \right)
\]
where $\kappa = \rho_0/\sigma$ and
\vspace{-0.1cm}
\[
\Psi(\phi) = 1 + \erf(\kappa \cos(\phi)) = 1 + \frac{2}{\sqrt{\pi}}\int_0^{\kappa \cos(\phi)} e^{-t^2} dt.
\]
Each of $A$, $B$ and $H$ can be computed by numerical integration using the above formula for $g(\phi)$.

>>>>

We will have particular use of complex random variables of the form $1 + X$ where $X$ is circularly symmetric.  Let $R \geq 0$ and $\Phi \in [0,2\pi)$ be real random variables satisfying $R e^{j\Phi} = 1 + X$.  The joint distribution of $R$ and $\Phi$ can be shown to be
\[
f(r,\phi) = \frac{r f_Z(\sqrt{r^2 - 2r\cos\phi + 1})}{2\pi\sqrt{r^2 - 2r\cos\phi + 1}}.
\]

@@

A key assumption in Theorem~\ref{thm:consistency} is that $G(x)$ is uniquely maximised at $x = 0$ for $x \in [-\pi, \pi)$.  %This assumption asserts that $G(x) \leq G(0)$ for all $x \in [-\pi, \pi)$ and that if $\{x_i\}$ is a sequence of numbers from $[-\pi,\pi)$ such that $G(x_i) \rightarrow G(0)$ as $i \rightarrow \infty$ then $x_i \rightarrow 0$ as $i \rightarrow \infty$.  
Although we will not prove it here, this assumption is not only sufficient, but also necessary, for if $G(x)$ is uniquely maximised at some $x \neq 0$ then $\sfracpart{\theta_0 - \hat{\theta}}_\pi \rightarrow x$ almost surely as $L\rightarrow\infty$, while if $G(x)$ is not uniquely maximised then $\sfracpart{\theta_0 - \hat{\theta}}_\pi$ will not converge.  One can check that the assumption holds when $w_1$ is circularly symmetric and normally distributed.  %We will not attempt to further classify those distributions for which the assumption holds here.
%The next proposition describes a class of circularly symmetric distributions for which $G(x)$ is uniquely maximised at $x = 0$.  The zero mean complex Gaussian distribution with independent real and imaginary parts is in this class.  We omit the proof due to space constraints.

@@

Let the noise sequence $\{w_i\}$ be complex Gaussian with independent real and imaginary parts having zero mean and variance $\sigma^2$.  The joint density function of the real and imaginary parts is
\[
\frac{1}{2\pi\sigma^2}e^{-\frac{1}{2\sigma^2}(x^2 + y^2)}.
\]
Theorem~\ref{thm:consistency}~and~\ref{thm:normality} hold, and since the distribution of $w_1$ is circularly symmetric, the distribution of $R_1e^{j\Phi_1}$ is identical to the distribution of $1 + \frac{1}{\rho_0} w_1$.
%and the joint density function of the real and imaginary parts of $Z$ is
%\[
%p_Z(x,y) = \rho_0^2 p( \rho_0 (x - 1), \rho_0 y ) = \frac{\kappa^2}{2\pi}e^{-\kappa^2(x ^2 - 2x + 1 + y^2) }
%\] 
%where $\kappa = \tfrac{\rho_0}{\sigma}$.  
It can be shown that
\[
%g(\phi) = \frac{\cos^2(\phi)}{4\sqrt{\pi}}\left( \frac{e^{-\kappa^2} }{\sqrt{\pi}} + \kappa \Psi(\phi)  e^{-\kappa^2\sin^2(\phi)}\cos(\phi) \right)
g(\phi) = \frac{\cos(\phi)}{2\pi}e^{-\frac{1}{2}\kappa^2} + \frac{\Psi(\phi)}{\kappa\sqrt{2\pi}}  e^{-\frac{1}{2}\kappa^2\sin^2(\phi)} \big(1 + \kappa^2\cos^2(\phi) \big)
\]
where $\kappa = \rho_0/\sigma$ and
\[
\Psi(\phi) = \frac{1}{2} + \frac{1}{2} \erf\left(\frac{\kappa \cos(\phi)}{\sqrt{2}}\right)
\]
and $\erf(x) = \frac{2}{\sqrt{\pi}}\int_0^{x} e^{-t^2} dt$ is the error function.  The value of $A_1, A_2, B_1$ and $B_2$ can be efficiently computed by numerical integration using these formula.
